\documentclass[aspectratio=169]{beamer}
\beamertemplatenavigationsymbolsempty
%\includeonlyframes{current}
\usefonttheme{professionalfonts}
%\usepackage{newtxtext,newtxmath}
\usepackage{animate}
\usepackage{graphicx}
\usepackage[labelformat=empty]{caption}
\usepackage{beamerthemesplit}
\usepackage{textpos}
\usepackage[percent]{overpic}
\usepackage{multirow}
\usepackage{array}
\usepackage{hhline}
\usepackage{siunitx}
\usepackage{comment}
\usepackage{tikz}
\usepackage{transparent}
\usepackage{soul}
%\usepackage{enumitem}
%\usepackage{transparent}
%\usepackage[orientation=landscape,size=custom,width=16,height=9,scale=0.5,debug]{beamerposter} 

\newcommand{\conv}{\scalebox{0.6}{$\perp$}}
\newcommand{\como}{\scalebox{0.6}{$+$}}
\newcommand{\Var}{\mathrm{Var}}


\title{Bayesian distribution fitting}
\author{Charlie Wusuo Liu}
%\date{May 29, 2019}


\expandafter\def\expandafter\insertshorttitle\expandafter{%
	\insertshorttitle\hfill%
	\insertframenumber\,/\,\inserttotalframenumber}

%\setbeamercovered{%
	%	still covered={\opaqueness<1->{10}},  
	%	again covered={\opaqueness<1->{10}}}


\begin{document}

% ---- first slide is here. Do not delete or change this line (set for making R package)

\begin{frame}{Progress}

\begin{enumerate}
\tiny\item  Halfway done in refurbishing the document on nonstationary covariance model.\medskip

\begin{itemize}
\tiny\item  Easy introduction to clients. Analogy to low dimensional embedding.\medskip

\tiny\item \tiny Justify why we chose cluster centers as kernel centers.\medskip
\end{itemize}

\tiny\item Refined the C++ codebase of \texttt{NGFMfitDistr}, \texttt{keyALGs}, \texttt{keyALGsExt}.\medskip

\begin{itemize}
\tiny\item Studied a lot about C++20. Familiarized with template meta programming for pushing compile time computation.\medskip

\tiny\item Implemented a memory pool that can recycle \texttt{std::vector} containers of any type in the most parsimonious manner. It will substantially reduce the memory footprint in all my current and future C++ applications, and change the way I approach problems --- from a more object-oriented mindset to a more functional one.\medskip

\begin{itemize}
\tiny\item This problem has been lingering in my head for 8 years.\medskip

\tiny\item Attempted to solve it more than a year ago but to little avail.\medskip

\tiny\item The practice will probably be frowned upon by C++ community as it does not entirely conform C++ standard. However, with sufficient pretests in the pool constructor, the computing platform will conclude if the software can be supported in compile time.\medskip
\end{itemize}
 
\end{itemize}

\tiny\item Briefly communicated Syed about LASSO. Next week they might need me to review the methodology or to run their Mexico model.

\end{enumerate}

\end{frame}

\end{document}
















